% Xiang Cai's Resume
% Created: Oct. 22 2010
% Last Modified: Nov. 14 2022

\documentclass[11pt,oneside]{article}
\usepackage{geometry}
\usepackage{verbatim}
\usepackage{xspace}
\usepackage{float}
\usepackage[T1]{fontenc}
\usepackage[colorlinks=false,linkcolor=black]{hyperref}
\def\pdfBorderAttrs{/Border [0 0 0] } 
\pagestyle{empty}
\geometry{letterpaper,tmargin=.5in,bmargin=.5in,lmargin=.5in,rmargin=.5in,headheight=0in,headsep=0in,footskip=.3in}

\setlength{\parindent}{0in}
\setlength{\parskip}{0in}
\setlength{\itemsep}{0in}
\setlength{\topsep}{0in}
\setlength{\tabcolsep}{0in}

% Name and contact information
\newcommand{\name}{Xiang Cai, Ph.D.\xspace}
\newcommand{\addrlinea}{24 Iroquois Rd\xspace}
\newcommand{\addrlineb}{Arlington, MA, 02476, USA\xspace}
\newcommand{\phone}{\hfill \textbf{Mobile: }(631)680-8544\xspace}
\newcommand{\email}{\hfill \textbf{Email: }xcai.stonybrook@gmail.com\xspace}
\newcommand{\cvphone}{\textit{(631)680-8544}\xspace}
\newcommand{\cvemail}{\textit{xcai.stonybrook@gmail.com}\xspace}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% New commands and environments

% This defines how the name looks
\newcommand{\bigname}[1]{
	\begin{center}\fontfamily{phv}\Huge{#1}\end{center}
}

% This defines contact info style
\newcommand{\contact}[1]{
	\begin{flushleft}\fontfamily{phv}\selectfont\Huge\Large#1\end{flushleft}
}

\newenvironment{ressection_empty}[1]{
%	\vspace{4pt}
	\vspace{-1pt}
	{\fontfamily{phv}\selectfont\Large#1}
	
	\vspace{-8pt} \rule{\textwidth}{.5pt}
}

% A ressection is a main section (<H1>Section</H1>)
\newenvironment{ressection}[1]{
%	\vspace{4pt}
%	\vspace{-1pt}
	{\fontfamily{phv}\selectfont\Large#1}
	
	\vspace{-8pt} \rule{\textwidth}{.5pt}
	
	\vspace{-4pt}
	\begin{itemize}
	\vspace{.5pt}
}{
	\end{itemize}
}

% A resitem is a simple list element in a ressection (first level)
\newcommand{\resitem}[1]{
	\vspace{2pt}
	\item \begin{flushleft} #1 \end{flushleft}
}

% A ressubitem is a simple list element in anything but a ressection (second level)
\newcommand{\ressubitem}[1]{
	\vspace{-4pt}
	\item \begin{flushleft} #1 \end{flushleft}
}

% A resbigitem is a complex list element for stuff like jobs and education:
%  Arg 1: Name of company or university
%  Arg 2: Location
%  Arg 3: Title and/or date range
\newcommand{\resbigitem}[3]{
	\vspace{-5pt}
	\item
	\textbf{#1} --- #2 \\
	{#3}
}

\newcommand{\resbigitemb}[2]{
	\vspace{-5pt}
	\item
	\textbf{#1} --- #2
}

% This is a list that comes with a resbigitem
\newenvironment{ressubsec}[3]{
	\resbigitem{#1}{#2}{#3}
	\vspace{-4pt}
	\begin{itemize}
}{
	\end{itemize}
}

\newenvironment{ressubsecb}[2]{
	\resbigitemb{#1}{#2}
	\vspace{-4pt}
}

% Same as ressubsec, but no item is required
\newenvironment{ressubsec_empty}[3]{
	\resbigitem{#1}{#2}{#3}
	\vspace{-2pt}
}


% This is a simple sublist
\newenvironment{reslist}[1]{
	\resitem{\textbf{#1}}
	\vspace{-5pt}
	\begin{itemize}
}{
	\end{itemize}
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Now for the actual document:

\begin{document}

\fontfamily{ppl} \selectfont

\begin{comment}
% begin coverletter
\bigname{\name}

\vspace{-8pt} \rule{\textwidth}{1pt}

\vspace{8 pt}

\begin{center}
\addrlinea \\
\addrlineb \\
\cvphone \\
\end{center}

\vspace{30pt}

December 12, 2013

\vspace{8pt}
Recruitment Team

\textit{Company, Inc.}

\textit{address}

\vspace{30pt}
Dear Hiring Executive,

\vspace{8pt}
I am writing in response to your recent advertisement for a Research Scientist
position (job id \#12345) on your website. Based on my background and experience, I believe I am
a strong candidate for the position.

\vspace{8pt}

\begin{table}[h]
\centering
\begin{tabular}{p{10cm}p{1cm}p{10cm}}
\textbf{YOUR NEEDS}	&	&	\textbf{MY QUALIFICATION}	\\
a	&	&	aa	\\
b	&	&	bb	\\

\end{tabular}
\end{table}

\vspace{8pt}
Thank you for your considerations. If you would like to discuss further about
my qualifications, please do not hesitate to contact me via email at 
\cvemail  or via telephone at \cvphone. I look forward to
talking with you!

\vspace{8pt}
Sincerely yours,

\vspace{30pt}
Xiang Cai

\vspace{30pt}
\textit{Attached: resume}

\newpage

% end of coverletter
\end{comment}

% Name with horizontal rule
\bigname{\name}

\vspace{-8pt} \rule{\textwidth}{1pt}

%\vspace{-1pt} {\small\itshape \addr \hfill \phone; \email}

%\vspace{8 pt}

%\contact{Contact Information}
\vspace{-6pt}
\begin{table}[h]
\begin{tabular}[h]{p{0.5\textwidth}p{0.5\textwidth}}
\addrlinea & \phone \\
\addrlineb & \email \\
\end{tabular}
\end{table}

\vspace{-4pt}

%\begin{ressection}{Objective}

%	\resitem{Obtain a full time job in the area of Software Engineering}

%\end{ressection}

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Work Experience}
    \vspace{-5pt}
    \begin{flushleft}
        {\fontfamily{serif}\selectfont\Large\bf{{Twitter}\hfill{Cambridge, MA}}}
    \end{flushleft}
    \vspace{-16pt}
    \item {\emph{\textbf{Senior Software Engineer} (Learning Streams Platform Team)} \hfill\emph{October 2021 -- November 2022}}
    \vspace{-4pt}
    \begin{itemize}
        \begin{small}
            \resitem{Started the transition into the Tech Lead role.}
            \resitem{Oversaw a multi-team effort to integrate critical server side metadata into event logs, which provided better quality user signals to serve more relevant content to end users and ultimately improved our app engagement by 0.1\%.}
            \resitem{Improved a data ingestion service that processes around 10 million events per second to ingest data in real time to Kafka. (\textbf{Scala, Kafka})}
    		\resitem{Collaborated with multiple cross-functional teams and finished a multi-year effort to deprecate an event logging service, cutting the cost by \$30,000 per month.}
    		\resitem{Designed and implemented a self-serving data governance service that is essential for event ownership management, user privacy and traffic control. (\textbf{Scala, MySQL.})}
    		\resitem{Contributed to the design and implementation of a real-time event ingestion pipeline that provides critical data to analytic systems and ML model training downstream. (\textbf{Scala, Kafka, BigQuery, PubSub, Terraform.})}
    	\end{small}
	\end{itemize}
	
    \item {\emph{\textbf{Senior Software Engineer} (Video Data Infrastructure Team)} \hfill\emph{December 2019 -- October 2021}}\vspace{-8pt}
    \item {\emph{\textbf{Software Engineer II} (Video Data Infrastructure Team)} \hfill\emph{April 2018 -- December 2019}}
    \vspace{-4pt}
    \begin{itemize}
        \begin{small}
            \resitem{Prototyped a metrics computation PoC using Airflow running on GCP. (\textbf{Python})}
    		\resitem{Contributed to the design and implementation of moving the media event aggregation infrastructure from on-prem to GCP. (\textbf{Dataflow, BigQuery, BigTable, PubSub.})}
    		\resitem{Oversaw the Personal Data Protection work on the VDI team and made sure the 10+ services and datasets we own were compliant with global regulation laws. (GDPR, etc.)}
    	\end{small}
	\end{itemize}
	
	\item {\emph{\textbf{Tech Lead, Software Engineer II} (Media Monetization Team)} \hfill\emph{March 2017 -- April 2018}}\vspace{-8pt}
    \item {\emph{\textbf{Software Engineer II} (Media Monetization Team)} \hfill\emph{September 2014 -- March 2017}}
    \vspace{-4pt}
    \begin{itemize}
        \begin{small}
    		\resitem{Built, maintained and improved services that were responsible for computing and serving various video metrics, including the video view counts shown on Twitter videos. (\textbf{Scala, Scalding.})}
    		\resitem{Designed and implemented a data validation system that monitored video event quality. (\textbf{Python, Presto.})}
    	\end{small}
	\end{itemize}
	
	\vspace{5pt}
    {\fontfamily{serif}\selectfont\Large\bf{{Hewlett-Packard Labs}\hfill{Princeton, NJ}}}
    \vspace{-2pt}
    \item 
        {\emph{\textbf{Research Associate Intern}}}\hfill\emph{June 2012 -- August 2012}
    \vspace{-4pt}
    \begin{itemize}
        \begin{small}
            \resitem{Conducted large scale data analysis on passive DNS traffic to find malicious command-and-control servers.}
			\resitem{Implemented a prototype system for detecting malicious URLs using Java.}
    	\end{small}
	\end{itemize}
\end{ressection}

\vspace{5pt}
\begin{ressection_empty}{Technical Skills}
\vspace{-10pt}
\begin{table}[H]
\begin{tabular}[h]{p{0.4\textwidth}p{0.6\textwidth}}
\textbf{Programming Languages:} & \textbf{Scala} (proficient, 8+ years of experience), \textbf{Python} (proficient, 3+ years of experience), \textbf{C/C++, Java, MySQL} (intermediate), \textbf{shell} (beginner)	\\[1.5pt]
\textbf{Platforms \& Development Tools:} & BigQuery, BigTable, Kafka, PubSub, MapReduce, git, IntelliJ  \\[1.5pt]
\textbf{Background:} & Big Data Analysis, Data Pipeline, Machine Learning, Security and Privacy \\
\end{tabular}
\end{table}
\vspace{-8pt}

%	\vspace{-4pt}
%	\resitem{
%		Operating Systems: \textbf{Linux (Ubuntu)} (4+ years of experience)
%	}

%	\resitem{Broad and diversified background in \textbf{System Programming},
%		\textbf{Algorithms}, \textbf{Software Development} and
%			\textbf{Computer Security}. Specialization in \textbf{System
%				Security} and \textbf{Network Security}. Excellent troubleshooting/problem solving skills.
%	}

\end{ressection_empty}

\vspace{40pt}
\begin{ressection}{Education}
    \vspace{-5pt}
    \begin{flushleft}
        {\fontfamily{serif}\selectfont\Large\bf{{Stony Brook University}\hfill{Stony Brook, NY}}}
    \end{flushleft}
    \vspace{-15pt}
    \item {\emph{\textbf{Ph.D.} in Computer Science (GPA:3.93/4)} \hfill\emph{September 2007 -- August 2014}}
    \vspace{-4pt}
    \begin{itemize}
        \begin{small}
            \resitem{Research focused on \textbf{System Security, Network Security} and \textbf{Privacy.}}
    	\end{small}
	\end{itemize}
	
	%\begin{ressubsec}{Stony Brook University}{}{\emph{\textbf{Ph.D.} in Computer Science (GPA:3.93/4)} \hfill\emph{September 2007 -- August 2014}}
	%	\ressubitem{Research focuses on \textbf{System Security, Network Security} and \textbf{Privacy.}
		%	\begin{small}
		%		\textit{} 
		%	\end{small}
		%}
		
%		\ressubitem{Core Courses:
%			\begin{small}
%				\textit{Operating Systems; Analysis of Algorithms; Theory of
%					Computation; Theory of Database Systems; Fundamental of
%						Computer Networks} 
%			\end{small}
%		}
%		\ressubitem{Candidate Exam Report:
	%		\href{http://docs.google.com/fileview?id=0Byne4VTOYpXPMGFjMzM5NWQtZWNiMC00M2Y2LThiNjktOTdmNjk4ODY2N2Rm&hl=en}
	%		{
%			\begin{small}
%				\textit{Type based Security Verification and Program Transformation}
%			\end{small}
%			}
%		}                                                                     
%	\end{ressubsec}

    \vspace{-10pt}
    \begin{flushleft}
        {\fontfamily{serif}\selectfont\Large\bf{{University of Sciences \& Technology of China}\hfill{Hefei, Anhui, China}}}
    \end{flushleft}
    \vspace{-15pt}
    \item {\emph{\textbf{B.E.} in Computer Science (GPA:3.83/4.3)} \hfill\emph{September 2003 - July 2007}}

%	\vspace{-4pt}
%	\begin{ressubsec_empty}{University of Sciences \& Technology of
%		China (USTC)}{Hefei, Anhui, China}{\textbf{B.E.} in Computer
%			Science (GPA:3.83/4.3) \hfill\textbf{September 2003 - July 2007}}
%	\end{ressubsec_empty}


\end{ressection}

\begin{comment}
\begin{ressection}{Research Projects}

	\resitem{\textbf{Website fingerprinting defenses.} Aug.
		2012. \hfill\textbf{[C++/ruby/python/MySQL]} 
		\vspace{-2pt}
		\begin{small}
		\vspace{-2pt}
		\begin{itemize}
		\item
		Developed bounds on the trade-off between security and
		bandwidth overhead.
		\item
		Compared schemes with different
		security/overhead trade-offs by comparing how close they are
		to the lower bound. 
		\item
		Refined, implemented, and evaluated
		the Congestion-Sensitive BuFLO scheme, which has high overhead (around 2.3-2.8x) but can
		get 6x closer to the bandwidth/security trade-off lower bound
		than Tor or plain SSH.
		\end{itemize}
		
		\end{small}				
	}
	\vspace{-4pt}
	\resitem{\textbf{Website fingerprinting attacks on Tor.} May.
		2011. \hfill\textbf{[C++/Java/ruby/MySQL]} 
		\vspace{-2pt}
		\begin{small}
		\vspace{-2pt}
		\begin{itemize}
		\item		
		Proposed and implemented two new website fingerprinting
			attacks on the Tor anonymity system.
		\item	
			Our attack outperformed recently-published fingerprinting attacks on Tor.
		\item			
			Source code: \textbf{git@github.com:xiang-cai/fingerprinting\_attack\_code.git}
		
		\end{itemize}		
		\end{small}				
	}

	\vspace{-4pt}
	\resitem{\textbf{A novel machine registration procedure.} Dec. 
		2010. \hfill\textbf{[PHP/MySQL]}
		\vspace{-2pt}
		\begin{small}
		\vspace{-2pt}
		\begin{itemize}
		\item
		Designed a novel online machine
			registration system. Users can register their computers to
			certain service providers (e.g. Banks, SNS websites) by
			visiting the registration website and then following specific
			instructions.
			\item
			Defeated phishing and MITM attacks.
		\end{itemize}
		\end{small}	
	}
			
	\vspace{-4pt}
	\resitem{\textbf{A C library for serializable file-system
				accessing.} Feb. 2010. \hfill\textbf{[C/C++/Shell]} 
		\vspace{-2pt}
		\begin{small}
		\vspace{-2pt}
		\begin{itemize}
		\item
		Proposed and implemented an
					easy-to-use, portable, provably-secure system for
					accessing UNIX file-systems without race conditions
					and that supported arbitrary sequences of operations
					within each pseudo-transaction and which had
					negligible overhead on a mail-server
					benchmark.
		\item					
		Source code: \textbf{git@github.com:xiang-cai/trace.git}
		\end{itemize}		
		\end{small}
	}
	
	\vspace{-4pt}
	\resitem{\textbf{Race attack on Unix File-Systems.} Oct. 2008. \hfill\textbf{[C/Shell]}
		\vspace{-2pt}
		\begin{small}
		\vspace{-2pt}
		\begin{itemize}
		\item		
		Defeated two proposed Unix file-system race
			condition defense mechanisms
		\item			
		Source code: \textbf{git@github.com:xiang-cai/race\_attack.git}
		\end{itemize}		
		\end{small}
	} 

%	\begin{ressubsec}{Stony Brook University, Computer Science
%		Department}{Stony Brook, NY}{Research Assistant under \textbf{Prof. Rob
%			Johnson}: Summer 2008--present}
%		\begin{small}	
%
%			\resitem{\textbf{Websites fingerprinting attacks on Tor. May.
%				2011}. 
%				\begin{small}
%				Proposed and implemented two new website fingerprinting
%					attacks on the Tor anonymity system. Our web page
%					classifier was novel in that, unlike all previous
%					classifiers, it completely ignored packet sizes. Despite
%					its simplicity, our attack outperformed 
%					recently-published fingerprinting attacks on Tor.
%					(C++/Java/ruby/MySQL)
%				\end{small}				
%			}
%
%			\resitem{\textbf{A novel machine registration procedure. Dec.
%				2010}. 
%				\begin{small}
%				Designed a novel online machine
%					registration system. Users can register their computers to
%					certain service providers (e.g. Banks, SNS websites) by
%					visiting the registration website and then following specific
%					instructions. This new process is as simple as most existing
%					machine registration procedures yet more secure. Phishing and MITM attacks against the
%					system are almost impossible. (PHP/MySQL)
%				\end{small}	
%			}
%					
%			\resitem{\textbf{A C library for serializable file-system
%						accessing. Feb. 2010}. 
%				\begin{small}
%				Proposed and implemented an
%							easy-to-use, portable, provably-secure system for
%							accessing UNIX file-systems without race conditions
%							and that supported arbitrary sequences of operations
%							within each pseudo-transaction and which had
%							negligible overhead on a mail-server
%							benchmark.(C/C++/Shell)
%				\end{small}
%			}
%			
%			\resitem{\textbf{Race attack on Unix File-Systems. Oct. 2008}.
%				\begin{small}
%				Defeated two proposed Unix file-system race
%					condition defense mechanisms. We argued that all
%					kernel-based dynamic race detectors must have a model of
%					the programs they protect or provide imperfect
%					protection.(C/Shell)
%				\end{small}
%			} 
%		\end{small}
%	\end{ressubsec}


%	\begin{ressubsec}{University of Sciences \& Technology of China}{National
%		High Performance Computing Center , Hefei, Anhui, China}{Undergraduate
%			Students Research Program, under \textbf{Prof. Liusheng Huang}:
%				July. 2006--Oct. 2006}
%		\begin{small}
%			\resitem{\textbf{Explored existing MAC protocols for Wireless Sensor Networks.}}
%	    	\resitem{\textbf{Optimized the performance of existing protocols under certain conditions.}}
%		\end{small}
%	\end{ressubsec}

\end{ressection}
\end{comment}

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{comment}
\begin{ressection}{Selected Course Projects}

	\resitem{\textbf{Very Simple Real File-System, Dec. 2008. [C/Kernel Programming]} 
		\begin{small}
		Implemented a very simple file-system with a group of three people, which supported regular file operations such as create, open, close, lookup, link, delete, etc.
		\end{small}
	}

	\resitem{\textbf{Linux Stackable File-system, Nov. 2008. [C/Kernel Programming]} 
		\begin{small}
		Implemented a stackable file system in Linux with a group of three people, which supported transparent
			file integrity checking.
		\end{small}
	}

	\resitem{\textbf{Adding A System Call To The Linux Kernel, Oct. 2008. [C/Kernel Programming]}
		\begin{small}
		Implemented a system call by adding a module to the Linux kernel (2.6.3.26), which can insert and delete data at user
			specified positions within a regular file.
		\end{small}		
	}

	\resitem{\textbf{WEP Cracking Project, Dec. 2007. [Java/C]} 
		\begin{small}
		Hacked and broke into a
		128 bit WEP protected wireless network by sniffing the headers of the packets being transmitted.
		\end{small}
	}
\end{ressection}


\begin{ressection}{Talks}
	\resitem{\textbf{Touching From a Distance: Website Fingerprinting
		Attacks and Defenses.} \begin{small}
		
		\textit{Invited talk to Symantec Research Labs. September 25th, 2012}. \textit{Conference presentation at ACM CCS, Raleigh, NC, October 2012}.
		\end{small}}

	\resitem{\textbf{Exploiting Unix File-System Races via Algorithmic
		Complexity Attacks.} \begin{small}
		
		\textit{Conference presentation at IEEE Symposium on Security and Privacy, Oakland, CA, May 2009}.
		\end{small}}
\end{ressection}

\begin{ressection}{Academic Activities}
	\resitem{\textbf{Security and Communication Networks 2013, } \begin{small}Invited journal reviewer.\end{small}
	}
\end{ressection}
\end{comment}

\begin{ressection}{Publications}
    \resitem{Selected publications are listed on this \href{https://scholar.google.com/citations?user=aLLW2YIAAAAJ&hl=en&oi=ao}{Google Scholar page}.}
\begin{comment}
	\resitem{Glove: A Bespoke Website Fingerprinting Defense. \begin{small} Rishab Nithyanand, \textbf{Xiang Cai} and Rob Johnson. \textit{Workshop on Privacy in the Electronic Society, Scottsdale, AZ, November 2014}.
	\end{small}}
	
	\resitem{CS-BuFLO: A Congestion Sensitive Website Fingerprinting Defense. \begin{small} \textbf{Xiang Cai}, Rishab Nithyanand and Rob Johnson. \textit{Workshop on Privacy in the Electronic Society, Scottsdale, AZ, November 2014}.
	\end{small}}
	
	\resitem{A Systematic Approach to Developing and Evaluating Website Fingerprinting Defenses. \begin{small} \textbf{Xiang Cai}, Rishab Nithyanand, Tao Wang, Rob Johnson and Ian Goldberg. \textit{ACM Conference on Computer and Communications Security, Scottsdale, AZ, November 2014}.
	\end{small}}
	
	\resitem{Effective Attacks and Provable Defenses for Website Fingerprinting. \begin{small} Tao Wang \textbf{Xiang Cai}, Rishab Nithyanand, Rob Johnson and Ian Goldberg. \textit{The 23rd USENIX Security Symposium, San Diego, CA, August 2014}.
	\end{small}}

	\resitem{Touching From a Distance: Website Fingerprinting
		Attacks and Defenses. \begin{small} \textbf{Xiang Cai}, Xincheng Zhang
			and Rob Johnson. \textit{ACM Conference on Computer and Communications Security, Raleigh, NC, October 2012}. %(Acceptance rate: 19\%, 81/426)
			\end{small}}

	\resitem{Exploiting Unix File-System Races via Algorithmic
		Complexity Attacks. \begin{small} \textbf{Xiang Cai}, Yuwei Gui, and
			Rob Johnson. \textit{IEEE Symposium on Security and Privacy,
				Oakland, CA, May 2009}. 
	%			(Acceptance rate: 10.2\%, 26/254)
				\end{small}}
\end{comment}
\end{ressection}
%%%%%%%%%%%%%%%%%%%%%%%%


\begin{comment}
%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Awards}
\resitem{\begin{small}Sep. 2007 New Graduate students Fellowship, Stony Brook University.\end{small}}
\resitem{\begin{small}Oct. 2006, Citigroup-CSTS Excellent Scholarship for undergraduate students.\end{small}}
\resitem{\begin{small}Oct. 2005, San Pu scholarship for undergraduate students.\end{small}}
\resitem{\begin{small}October 2004, Outstanding Student Scholarship (Grade 2), USTC.\end{small}}
\resitem{\begin{small}Nov. 2003, Second place in the English Debate Competition of USTC.\end{small}}
\end{ressection}
\end{comment}

\end{document}
